Open Science, Open Plant Pathology

### 2019-01-10 analysis/paper/paper.Rmd
Update figure 1, removes "_" from nodes

---
title: "Open Science, Open Plant Pathology"
author:
  - Adam H. Sparks
  - Emerson Del Ponte
  - Sydney Everhart
  - Zachary Foster
  - Niklaus J Grünwald
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/phytopathology.csl" # Insert path for the bib-style
abstract: |
  Open research practices have been highlighted extensively during the last ten years in many fields of study as essential standards needed to promote transparency and reproducibility of scientific results. In fact, scientific claims can only be evaluated based on how protocols, materials, equipment and methods were described; data were collected and prepared; and analyses conducted. Openly sharing protocols, data and computational code are central for current scholarly dissemination and communication, but in many fields, including Plant Pathology, adoption of these practices has been slow. We randomly selected 200 articles published from 2012 to 2016 across 21 journals representative of the pathology discipline, and assigned them scores reflecting their openness and reproducibility. We found that most of the articles failed to share data or code in a meaningful way. We propose that and open source tools for producing open and reproducible work and analysis is necessary and provide ideas and tools to promote reproducible practices among plant pathologists.
keywords: |
  open science; open data; reproducible research; FAIR data
highlights: |
  Open research practices are highlighted extensively in the broader scientific community. Our survey of 200 randomly selected articles from 2012 to 2016 indicates that we have work to do in this area as plant pathologists. 
---

@@

## A general workflow

@@

  node [shape = box, style = filled, fillcolor = grey80, width = 1.2]
  Binary_Code; Binary_File; Supplement

  node [shape = box, style = filled, fillcolor = grey70, width = 1.2]
  Source_Code;  Data_File; Pub_Repository;

  Question->Methodology->Data->Analysis
  Analysis->Manuscript
  Methodology->Description
  Methodology->Citation
  Methodology->Availability
  Manuscript->Supplement
  Data->Data_File->Pub_Repository
  Analysis->Binary_Code->Supplement
  Analysis->Source_Code->Pub_Repository
  Data->Binary_File->Supplement
  }
  ",
  width = 1000,
  height = 750
))

@@

## Status in Plant Pathology

@@

## Discussion

>>>>

---
title: "Open Science, Open Plant Pathology"
author:
  - Adam H. Sparks
  - Emerson Del Ponte
  - Sydney Everhart
  - Zachary Foster
  - Niklaus J Grünwald
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/phytopathology.csl" # Insert path for the bib-style
abstract: |
  Open research practices have been highlighted extensively during the last ten years in many fields of study as essential standards needed to promote transparency and reproducibility of scientific results. In fact, scientific claims can only be evaluated based on how protocols, materials, equipment and methods were described; data were collected and prepared; and analyses conducted. Openly sharing protocols, data and computational code are central for current scholarly dissemination and communication, but in many fields, including Plant Pathology, adoption of these practices has been slow. We randomly selected 200 articles published from 2012 to 2016 across 21 journals representative of the pathology discipline, and assigned them scores reflecting their openness and reproducibility. We found that most of the articles failed to share data or code in a meaningful way. We propose that using open source tools for producing open and reproducible work and analysis is necessary and provide ideas and tools to promote reproducible practices among plant pathologists.
keywords: |
  open science; open data; reproducible research; FAIR data
highlights: |
  Open research practices are highlighted extensively in the broader scientific community. Our survey of 200 randomly selected articles from 2012 to 2016 indicates that we have work to do in this area as plant pathologists with most articles scoring low in openness and reproduciblity.
---

@@

## Open science

Open science has become highlighted lately with many donors expecting data to be available (XXXX) and other scientists interested in sharing and collaborating more widely.

# A general workflow

@@

  node [shape = box, style = filled, fillcolor = grey80, width = 1.2]
  'Binary Code'; 'Binary File'; Supplement

  node [shape = box, style = filled, fillcolor = grey70, width = 1.2]
  'Source Code';  'Data File'; 'Public Repository';

  Question->Methodology->Data->Analysis
  Analysis->Manuscript
  Methodology->Description
  Methodology->Citation
  Methodology->Availability
  Manuscript->Supplement
  Data->'Data File'->'Public Repository'
  Analysis->'Binary Code'->Supplement
  Analysis->'Source Code'->'Public Repository'
  Data->'Binary File'->Supplement
  }
  ",
  width = 1000,
  height = 750
))

@@

# Status in Plant Pathology

@@

# Discussion
